The Transition from Massive Metal Free Stars to Dwarf Galaxies

### 2011-01-22 ms.tex
Finished a draft of halo properties evo. section.  Added table with halo z=7 properties.

A fraction of Pop III stars enrich the surrounding IGM when
they go supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}. The host
halo and the neighboring haloes are then enriched with this ejecta.
The blastwave expands to a radius of a few kpc \citep{Bromm03_SN,
  Wise08_Gal, Greif10} with approximately half of the ejecta falling
back into the adjacent filaments and haloes.  The blastwave may induce
star formation in nearby haloes through the compression of the gas
\citep{Shapiro87, Ferrara98, Mackey03}, and the timescales for metal
mixing into the dense gas are many dynamical times \citep{Cen08} for
shock velocities $\lsim 100~\kms$.

When star-forming gas reaches some `critical metallicity' $Z_{\rm
  cr}$, radiative cooling from metal fine-structure lines or
\hh~formation on dust grains becomes efficient, allowing cooling to $T
\lsim 100$ K \citep{Omukai05}.  The exact value of $Z_{\rm cr}$ has
been constrained to be between $10^{-6} \zsun$ and $10^{-3.5} \zsun$.
The lower limit applies if dust cooling is important in these
scenarios \citep{Omukai05, Schneider06_Frag, clark08}, and the upper
limit happens if metal line cooling in the gas-phase is the dominant
process \citep{Bromm01, 2009ApJ...691..441S}.  This metal-enriched gas
fragments and most likely forms stars with masses similar to
present-day stellar initial mass functions (IMF), marking the local
transition from Pop III to II star formation.  Intermediate to
these populations and possibly unique to high redshift, there exists a
mode of massive star formation that has a characteristic mass of $\sim
10 \Ms$ \citep{Larson98, Tumlinson07_IMF, 2009ApJ...691..441S}.  This
happens when cooling in metal-enriched gas is limited to the cosmic
microwave background (CMB) temperature $T_{\rm CMB} = 2.73 (1+z)$ K,
which can be significantly higher than the cores of typical molecular
clouds ($T \sim 10$ K).

@@

Over the past decade, these works have refined the general picture of
inhomogenous metal enrichment and the transition to Pop II star
formation, and here we give a brief overview of its development.
Considering only Pop III star formation, \citeauthor{Yoshida04}
calculated that Pop III stars can raise the mean metallicity to $-4.5
\lsim$ [Z/H]\footnote{We use the conventional notation, [Z/H] $\equiv
  \log(Z/H) - \log(Z_\odot/H_\odot)$.} $\lsim -3.5$ by redshift 15 in
the upper limit where all metal-free stars have $M = 200 \Ms$ and
produce PISNe.  Considering both Pop III and II star formation,
\citeauthor{Scannapieco03} found that the transition between the two
modes is a gradual process where both modes are coeval, confirmed by
most of the later works.  Because the host galaxies have small masses
and are subject to negative radiative feedback through photo-heating
and photo-dissociation, the minimum halo mass gradually increases with
the radiation background intensity, which
\citeauthor{Furlanetto05_Reion} found to delay metal enrichment and
place it closer to the epoch of reionization.  \citeauthor{Trenti09}
noted that underdense regions of the universe are still pristine at
$z=6$ with Pop III stars still forming at these late epochs.  This
group later expanded on these results to find that Pop II SFR becomes
dominant at $z>25$ in the buildup of a MW-type halo.  Furthermore they
stress the importance of a photo-dissociating radiation background
that reduces enrichment by PISNe and increases the importance of
metal-rich galactic outflows, where only $10^{-4} - 10^{-2}$ of PISN
ejecta ends up in EMP stars with $M > 0.9 \Ms$.

The Pop III IMF should play an important role in abundance patterns in
extremely metal poor (EMP) stars in the Milky Way (MW) halo and the
physics of reionization.  Using these data as constraints,
\citeauthor{Tumlinson06} found that Pop III IMFs with log-normal
distributions with mean masses between 8 and 42 \Ms~best fit the data.
Furthermore he concludes that EMP stars with [Z/H] $<$ --3 have
between 1 and 10 metal-free SN progenitors and the Pop III SFR is less
than 1\% of the total SFR at $z=6$.  \citeauthor{Karlsson08} use
observational data of EMP stars with their model to constrain the mass
fraction of Pop III stars that die with a PISN is less than 40 per
cent.  They also conclude that stars enriched primarily by PISNe have
[Ca/H] $\gsim$ --2.6, which could have been missed by some EMP
surveys.

@@

We treat Pop II star formation with the same prescription as
\citet{Wise09}, which is similar to the Pop III prescription but
without the \hh~fraction floor that is removed because the
metal-enriched gas can efficiently cool even in the presence of a
strong UV radiation field \citep[e.g.][]{Safranek10}.  This method is
effectively a modified version of the \citet{Cen92} method but
accounts for the fact that the molecular clouds are resolved.  In the
simulation, we define the molecular cloud as a sphere, centered on the
most dense cell, with a dynamical time $t_{\rm dyn} = 3$ Myr
(corresponding to an average density $\bar{\rho}_{\rm MC} \simeq
1000\mu \cubecm$) and a radius $R_{\rm MC}$.  In this sphere, a
fraction $c_\star = 0.07 f_{\rm cold}$ of the cold gas ($T < 10^3$ K)
is converted into a star particle with mass $m_\star = c_\star
(4\pi/3) \bar{\rho}_{\rm MC} R_{\rm MC}^3$.  We then replace the
sphere with a uniform density $\rho_{\rm MC} = (1 - c_\star) /
(Gt_{\rm dyn}^2)$ and temperature $T = 10^4$ K, which approximates the
initial stages of an \hii~region.  Similar to the Pop III treatment,
we merge any newly created particles within a radius $R_{\rm merge}$.
We set the minimum mass of a star particle to $m_{\rm \star, min} =
1000 \Ms$.  If the initial mass does not exceed $m_{\rm \star, min}$,
the star particle does not provide any feedback and continues to
accrete until it reaches $m_{\rm \star, min}$.  The star particles
live for 20 Myr, the maximum lifetime of an OB star.  These stars
generate the majority of the ionizing radiation and SNe feedback in
stellar clusters, thus we ignore any feedback from lower mass stars.

@@

The radiation field is evolved with adaptive ray tracing
\citep{Abel02_RT, Wise10} that is based on the HEALPix framework
\citep{HEALPix} and is coupled self-consistently to the hydrodynamics.
Each star particle is a point source of hydrogen ionizing radiation
with the ionizing luminosity equally split between 48 initial rays
(HEALPix level 2).  We use a mono-chromatic spectrum for the radiation
with the energy $E_{\rm ph}$ equaling the luminosity-weighted photon
energy of the spectrum.  For a cosmological simulation that focuses on
galaxies, this does not significantly affect the overall galactic
dynamics \citep[see Sec. 6.3 in][]{Wise10}.  We do not consider helium
singly- and doubly-ionizing radiation.  As the rays propagate from the
source or into a high resolution AMR grid, they are adaptively split
into 4 child rays, increasing the angular resolution of the solution,
when the solid angle of the ray $\theta = 4\pi/(12 \times 4^{L})$ is
larger than 1/3 of the cell area, where $L$ is the HEALPix level.  We
model the \hh~dissociating radiation with an optically-thin, inverse
square profile, centered on all star particles.  In haloes with $M
\gsim 10^8 \Ms$, the \hh~column density may become large enough to
self-shield itself from LW radiation \citep{Wise08_Gal}.  Thus we may
be underestimating the SFRs in our work.

@@

\begin{figure}
  \plotone{uvb.eps}
  \caption{\label{fig:uvb} Time evolution of the Lyman-Werner
    background, calculated with the \citet{Wise05} model.}
\end{figure}

@@

\begin{enumerate}
\item Radiative cooling from metal species.  We calculate a cooling
  curve with CLOUDY \citep{CLOUDY} and use the method of
  \citep{2008MNRAS.385.1443S}.  Solar abundances were used in the
  cooling curve.  It is tabulated based on density, temperature,
  electron fraction, and total metallicity.
\item A critical metallicity of [Z/H] = --5 and --6, accounting for
  the case where dust cooling can induce low-mass fragmentation in
  these lower metallicities \citep{Omukai05, Schneider06_Frag}.
\item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.  Using
  the abundance patterns of EMP stars and reionization as constaints,
  the data are best fit with IMFs favoring stars with masses between
  20--130 \Ms \citep{Umeda03, Tumlinson06}.
\item Lyman-Werner radiation background.  We use the semi-analytical
  model of \citet{Wise05}, updated with the 7-year WMAP parameters and
  optical depth to Thompson scattering, to calculate the LW background
  intensity, plotted in Figure \ref{fig:uvb}.  In this semi-analytical
  model, we use a Pop III stellar mass of 100 \Ms, star formation
  efficiency of 0.005, and escape fraction of 0.2 \citep{Wise09}.  The
  LW radiation from point sources are added to the background.  The
  intensity decreases after $z \sim 14$ because Pop II star formation
  becomes dominant, which produce less LW specific luminosity than Pop
  III stars that have surface temperatures of $T = 10^5$ K.  For
  computational convenience, we fit the background evolution with the
  function
%
  \begin{equation}
    \label{eqn:uvb}
    \log J_{21}(z) = A + Bz - Cz^2 + Dz^3 - Ez^4,
  \end{equation}
%
  where $(A,B,C,D,E) = (-2.356, 0.4562, 0.02680, 5.882 \times 10^{-4},
  -5.056 \times 10^{-6})$ and $J_{21}$ is the specific intensity in
  units of $10^{-21}$ \emis.  This fits the
  model data within 1\% in $6 \le z \le 30$ and is consistent with
  $J_{21}$ values in \citet{Trenti09_SFR}.
\item Pop II star formation only.  This model is useful to study the
  importance of treating Pop III star formation as single stars and
  their pair-instability and Type II SNe.
\item Pop II star formation only and no molecular hydrogen cooling.
  This model provides a good comparison to larger scale simulations
  where it is not computationally feasible to consider \hh~cooling or
  resolve the necessary scales for Pop III star formation.
\end{enumerate}

@@

Here we present the gaseous and stellar evolution of the high-redshift
dwarf galaxies that form in our simulations.  To illustrate its global
properties, we show the density-weighted projections of gas density,
temperature, and metallicity at redshifts 15, 12, 10, 8, and 7 in
Figure \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of
IGM over this redshift range, where the ionized fraction is 0.XX at
$z=7$.  The metallicity projections show the growth of metal-enriched
bubbles, starting first with enrichment from Pop III stars.  Then as
time progresses, the haloes enriched within these bubbles above $Z_{\rm
  cr}$ transition to Pop II star formation, enriching their host halo
and surrounding IGM.  In Fig. \ref{fig:mass_fn}, we show the halo mass
function, agreeing well with the analytic halo mass function of
\citet{Warren06}.  We identify the haloes with a friends-of-friends
(FOF) algorithm \citep{Davis85}.  The excess of low-mass haloes below
$M_{\rm DM} = 2 \times 10^6 \Ms$ is most likely associated with the
biased region in the lower-right region in the projections.
Furthermore, the uncertainities in different analytic halo mass
functions \citep[e.g., see][for a comparison]{Reed07} and halo
identification are comparable than these differences.  Also in this
Figure, we display the galaxy luminosities with respect to halo DM
mass found with the FOF halo finder.  Our fidicual model contains 38
galaxies with a total of 3640 Pop II star clusters and captures the
formation of 333 Pop III stars.  Note that the most massive halo
($M_{\rm DM} = 5.2 \times 10^8 \Ms$) is undergoing a starburst at
$z=7$ and has a high $M/L = 3$.  The lower mass galaxies show a spread
in M/L over two orders of magnitude, similar to the observations of
local dSph galaxies \citep[e.g.][]{Strigari08}.

We split our presentation into two sets of analyses.  In one, we focus
on the evolution of the individual halo and galaxy properties of the
10 most massive haloes at $z=7$ to better understand their formation
process and progenitors.  Second, we analyze the statistics of the
star formation and metal enrichment in all 38 galaxies.  We start by
presenting the change in the global halo properties, followed by their
metal enrichment histories.  Lastly we detail their star formation
histories, metallicity distribution functions, and star formation
rates.

\subsection{Halo mass evolution}

To get a visual sense of the mass accretion and metal enrichment
history of the 10 most massive haloes, we show their density-weighted
projections of gas density, temperature, and composite Pop II+III
metallicity at redshifts 7, 8, and 10 in
Fig. \ref{fig:z7-mosaic}--\ref{fig:z10-mosaic}, respectively.  One
common feature of all of the halos represented in these Figure is that
they are embedded in a preheated IGM with the exception of Halo 7 at
$z=10$.  Prior radiative feedback in either the host or nearby halos
created \hii~regions that encompass these halos.  For \hii~regions
without sustained star formation, these so-called relic \hii~regions
recombine and radiatively cool down to $T = 10^3$ K.  Within the
virial radius, one can see that our simulations capture the
multi-phase ISM.  In the density projections, the effects of
photo-evaporation and cloud crushing are clearly seen, which are
caused by the stellar radiative and mechanical feedback, respectively.
The filaments adjacent to the halos are photo-heated to $T = 1-3
\times 10^4$ K, and then their gas escapes into the IGM no longer
being pressure equilibrium with the gravitational potential of the
filament, i.e. Jeans smoothing.  Furthermore, neighboring halos are
photo-evaporated \citep[see][for the level of halo
photo-evaporation]{Wise08_Reion}, resulting in the suppression of
gas-rich satellite haloes.  A good illustration of photo-evaporation
in progress is the cometary structure in the bottom-center of the
density projection of Halo 4 at $z=7$.

\li Something is wrong with the progenitor finder with Halo 9 at $t =
500$ Myr.  See the extreme jump in mass and decrease in gas fraction?

In Fig. \ref{fig:massevo}, we show the total halo mass $M_{\rm tot}$,
stellar mass $M_\star$, and gas fraction $f_{\rm gas} = M_{\rm gas} /
M_{\rm tot}$ of the most massive halos as a function of time.  We
define the halo as a sphere with a radius $r_{200}$, centered on the
DM center-of-mass, with an overdensity of 200 times the cosmic mean
density.  We identify the progenitors of these halos by searching for
the halo in the previous output with the greatest number of shared
particles (all particles in \enzo~have unique identification numbers).
The mass accretion histories of the halos are not atypical from ones
found in cosmological simulations with periods of smooth accretion
from the IGM and filaments with major mergers occasionally occurs,
appearing as jumps in $M_{\rm halo}(z)$.

Even from these visual representations of the data, it is clear that
almost all of the halos are gas-poor with outflows from Pop III star
formation and PISNe having the greatest effect.

@@

\begin{figure}
  \plottwo{history0.eps}{history5.eps}
  \caption{\label{fig:massevo} Mass evolution.}
\end{figure}

@@

>>>>

A fraction of Pop III stars enrich the surrounding IGM when
they go supernova, which can happen in stars $\la 40~\Ms$ in Type II
supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}. The host
halo and the neighboring haloes are then enriched with this ejecta.
The blastwave expands to a radius of a few kpc \citep{Bromm03_SN,
  Wise08_Gal, Greif10} with approximately half of the ejecta falling
back into the adjacent filaments and haloes.  The blastwave may induce
star formation in nearby haloes through the compression of the gas
\citep{Shapiro87, Ferrara98, Mackey03}, and the timescales for metal
mixing into the dense gas are many dynamical times \citep{Cen08} for
shock velocities $\la 100~\kms$.

When star-forming gas reaches some `critical metallicity' $Z_{\rm
  cr}$, radiative cooling from metal fine-structure lines or
\hh~formation on dust grains becomes efficient, allowing cooling to $T
\la 100$ K \citep{Omukai05}.  The exact value of $Z_{\rm cr}$ has
been constrained to be between $10^{-6} \zsun$ and $10^{-3.5} \zsun$.
The lower limit applies if dust cooling is important in these
scenarios \citep{Omukai05, Schneider06_Frag, clark08}, and the upper
limit happens if metal line cooling in the gas-phase is the dominant
process \citep{Bromm01, 2009ApJ...691..441S}.  This metal-enriched gas
fragments and most likely forms stars with masses similar to
present-day stellar initial mass functions (IMF), marking the local
transition from Pop III to II star formation.  Intermediate to
these populations and possibly unique to high redshift, there exists a
mode of massive star formation that has a characteristic mass of $\sim
10 \Ms$ \citep{Larson98, Tumlinson07_IMF, 2009ApJ...691..441S}.  This
happens when cooling in metal-enriched gas is limited to the cosmic
microwave background (CMB) temperature $T_{\rm CMB} = 2.73 (1+z)$ K,
which can be significantly higher than the cores of typical molecular
clouds ($T \sim 10$ K).

@@

Over the past decade, these works have refined the general picture of
inhomogenous metal enrichment and the transition to Pop II star
formation, and here we give a brief overview of its development.
Considering only Pop III star formation, \citeauthor{Yoshida04}
calculated that Pop III stars can raise the mean metallicity to $-4.5
\la$ [Z/H]\footnote{We use the conventional notation, [Z/H] $\equiv
  \log(Z/H) - \log(Z_\odot/H_\odot)$.} $\la -3.5$ by redshift 15 in
the upper limit where all metal-free stars have $M = 200 \Ms$ and
produce PISNe.  Considering both Pop III and II star formation,
\citeauthor{Scannapieco03} found that the transition between the two
modes is a gradual process where both modes are coeval, confirmed by
most of the later works.  Because the host galaxies have small masses
and are subject to negative radiative feedback through photo-heating
and photo-dissociation, the minimum halo mass gradually increases with
the radiation background intensity, which
\citeauthor{Furlanetto05_Reion} found to delay metal enrichment and
place it closer to the epoch of reionization.  \citeauthor{Trenti09}
noted that underdense regions of the universe are still pristine at
$z=6$ with Pop III stars still forming at these late epochs.  This
group later expanded on these results to find that Pop II SFR becomes
dominant at $z>25$ in the buildup of a MW-type halo.  Furthermore they
stress the importance of a photo-dissociating radiation background
that reduces enrichment by PISNe and increases the importance of
metal-rich galactic outflows, where only $10^{-4} - 10^{-2}$ of PISN
ejecta ends up in EMP stars with $M > 0.9 \Ms$.

The Pop III IMF should play an important role in abundance patterns in
extremely metal poor (EMP) stars in the Milky Way (MW) halo and the
physics of reionization.  Using these data as constraints,
\citeauthor{Tumlinson06} found that Pop III IMFs with log-normal
distributions with mean masses between 8 and 42 \Ms~best fit the data.
Furthermore he concludes that EMP stars with [Z/H] $<$ --3 have
between 1 and 10 metal-free SN progenitors and the Pop III SFR is less
than 1\% of the total SFR at $z=6$.  \citeauthor{Karlsson08} use
observational data of EMP stars with their model to constrain the mass
fraction of Pop III stars that die with a PISN is less than 40 per
cent.  They also conclude that stars enriched primarily by PISNe have
[Ca/H] $\ga$ --2.6, which could have been missed by some EMP
surveys.

@@

We treat Pop II star formation with the same prescription as
\citet{Wise09}, which is similar to the Pop III prescription but
without the \hh~fraction floor that is removed because the
metal-enriched gas can efficiently cool even in the presence of a
strong UV radiation field \citep[e.g.][]{Safranek10}.  This method is
effectively a modified version of the \citet{Cen92} method but
accounts for the fact that the molecular clouds are resolved.  In the
simulation, we define the molecular cloud as a sphere, centered on the
most dense cell, with a dynamical time $t_{\rm dyn} = 3$ Myr
(corresponding to an average density $\bar{\rho}_{\rm MC} \simeq
1000\mu \cubecm$) and a radius $R_{\rm MC}$, where $\mu$ is the mean
molecular weight.  In this sphere, a fraction $c_\star = 0.07 f_{\rm
  cold}$ of the cold gas ($T < 10^3$ K) is converted into a star
particle with mass $m_\star = c_\star (4\pi/3) \bar{\rho}_{\rm MC}
R_{\rm MC}^3$.  We then replace the sphere with a uniform density
$\rho_{\rm MC} = (1 - c_\star) / (Gt_{\rm dyn}^2)$ and temperature $T
= 10^4$ K, which approximates the initial stages of an \hii~region.
Similar to the Pop III treatment, we merge any newly created particles
within a radius $R_{\rm merge}$.  We set the minimum mass of a star
particle to $m_{\rm \star, min} = 1000 \Ms$.  If the initial mass does
not exceed $m_{\rm \star, min}$, the star particle does not provide
any feedback and continues to accrete until it reaches $m_{\rm \star,
  min}$.  The star particles live for 20 Myr, the maximum lifetime of
an OB star.  These stars generate the majority of the ionizing
radiation and SNe feedback in stellar clusters, thus we ignore any
feedback from lower mass stars.

@@

The radiation field is evolved with adaptive ray tracing
\citep{Abel02_RT, Wise10} that is based on the HEALPix framework
\citep{HEALPix} and is coupled self-consistently to the hydrodynamics.
Each star particle is a point source of hydrogen ionizing radiation
with the ionizing luminosity equally split between 48 initial rays
(HEALPix level 2).  We use a mono-chromatic spectrum for the radiation
with the energy $E_{\rm ph}$ equaling the luminosity-weighted photon
energy of the spectrum.  For a cosmological simulation that focuses on
galaxies, this does not significantly affect the overall galactic
dynamics \citep[see Sec. 6.3 in][]{Wise10}.  We do not consider helium
singly- and doubly-ionizing radiation.  As the rays propagate from the
source or into a high resolution AMR grid, they are adaptively split
into 4 child rays, increasing the angular resolution of the solution,
when the solid angle of the ray $\theta = 4\pi/(12 \times 4^{L})$ is
larger than 1/3 of the cell area, where $L$ is the HEALPix level.  We
model the \hh~dissociating radiation with an optically-thin, inverse
square profile, centered on all star particles.  In haloes with $M
\ga 10^8 \Ms$, the \hh~column density may become large enough to
self-shield itself from LW radiation \citep{Wise08_Gal}.  Thus we may
be underestimating the SFRs in our work.

@@

\begin{figure}
  \plotone{uvb.eps}
  \caption{\label{fig:uvb} Time evolution of the Lyman-Werner
    background in units of $J_{21} = 10^{-21}$ \emis, calculated with
    the \citet{Wise05} model.  See eq. (\ref{eqn:uvb}) for its
    functional fit.}
\end{figure}

@@

\begin{enumerate}
\item Radiative cooling from metal species.  We calculate a cooling
  curve with CLOUDY \citep{CLOUDY} and use the method of
  \citep{2008MNRAS.385.1443S}.  Solar abundances were used in the
  cooling curve.  It is tabulated based on density, temperature,
  electron fraction, and total metallicity.
\item A critical metallicity of [Z/H] = --5 and --6, accounting for
  the case where dust cooling can induce low-mass fragmentation in
  these lower metallicities \citep{Omukai05, Schneider06_Frag}.
\item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.  Using
  the abundance patterns of EMP stars and reionization as constaints,
  the data are best fit with IMFs favoring stars with masses between
  20--130 \Ms \citep{Umeda03, Tumlinson06}.
\item Lyman-Werner radiation background.  We use the semi-analytical
  model of \citet{Wise05}, updated with the 7-year WMAP parameters and
  optical depth to Thompson scattering, to calculate the LW background
  intensity, plotted in Fig. \ref{fig:uvb}.  In this semi-analytical
  model, we use a Pop III stellar mass of 100 \Ms, star formation
  efficiency of 0.005, and escape fraction of 0.2 \citep{Wise09}.  The
  LW radiation from point sources are added to the background.  The
  intensity decreases after $z \sim 14$ because Pop II star formation
  becomes dominant, which produce less LW specific luminosity than Pop
  III stars that have surface temperatures of $T = 10^5$ K.  For
  computational convenience, we fit the background evolution with the
  function
%
  \begin{equation}
    \label{eqn:uvb}
    \log J_{21}(z) = A + Bz - Cz^2 + Dz^3 - Ez^4,
  \end{equation}
%
  where $(A,B,C,D,E) = (-2.356, 0.4562, 0.02680, 5.882 \times 10^{-4},
  -5.056 \times 10^{-6})$ and $J_{21}$ is the specific intensity in
  units of $10^{-21}$ \emis.  This fits the
  model data within 1\% in $6 \le z \le 30$ and is consistent with
  $J_{21}$ values in \citet{Trenti09_SFR}.
\item Pop II star formation only.  This model is useful to study the
  importance of treating Pop III star formation as single stars and
  their pair-instability and Type II SNe.
\item Pop II star formation only and no molecular hydrogen cooling.
  This model provides a good comparison to larger scale simulations
  where it is not computationally feasible to consider \hh~cooling or
  resolve the necessary scales for Pop III star formation.
\end{enumerate}

@@

\input table1.tex

Here we present the gaseous and stellar evolution of the high-redshift
dwarf galaxies that form in our simulations.  To illustrate its global
properties, we show the density-weighted projections of gas density,
temperature, and metallicity at redshifts 15, 12, 10, 8, and 7 in
Fig. \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of
IGM over this redshift range, where the ionized fraction is 0.XX at
$z=7$.  The metallicity projections show the growth of metal-enriched
bubbles, starting first with enrichment from Pop III stars.  Then as
time progresses, the haloes enriched within these bubbles above $Z_{\rm
  cr}$ transition to Pop II star formation, enriching their host halo
and surrounding IGM.  In Fig. \ref{fig:mass_fn}, we show the halo mass
function, agreeing well with the analytic halo mass function of
\citet{Warren06}.  We identify the haloes with a friends-of-friends
(FOF) algorithm \citep{Davis85}.  The excess of low-mass haloes below
$M_{\rm DM} = 2 \times 10^6 \Ms$ is most likely associated with the
biased region in the lower-right region in the projections.
Furthermore, the uncertainities in different analytic halo mass
functions \citep[e.g., see][for a comparison]{Reed07} and halo
identification are comparable than these differences.  Also in this
Figure, we display the galaxy luminosities with respect to halo DM
mass found with the FOF halo finder.  Our fidicual model contains 38
galaxies with a total of 3640 Pop II star clusters and captures the
formation of 333 Pop III stars.  Note that the most massive halo
($M_{\rm DM} = 5.2 \times 10^8 \Ms$) is undergoing a starburst at
$z=7$ and has a high $M/L = 3$.  The lower mass galaxies show a spread
in M/L over two orders of magnitude, similar to the observations of
local dSph galaxies \citep[e.g.][]{Strigari08}.

We split our presentation into two sets of analyses.  In one, we focus
on the evolution of the individual halo and galaxy properties of the
10 most massive haloes at $z=7$ to better understand their formation
process and progenitors.  We list the global properties of these
haloes at $z = 7$ in Table \ref{tab:halos}.  Second, we analyze the
statistics of the star formation and metal enrichment in all 38
galaxies.  We start by presenting the change in the global halo
properties, followed by a description of their star formation
histories, metallicity distribution functions, and star formation
rates.  We then present their metal enrichment and lastly comment on
unique details of individual haloes.

\subsection{Time evolution of halo properties}

@@

To get a visual sense of the mass accretion and metal enrichment
history of the 10 most massive haloes, we show their density-weighted
projections of gas density, temperature, and composite Pop II+III
metallicity at redshifts 7, 8, and 10 in
Fig. \ref{fig:z7-mosaic}--\ref{fig:z10-mosaic}, respectively.  One
common feature of all of the halos represented in these Figures is
that they are embedded in a preheated IGM with the exception of Halo 7
at $z=10$.  Prior radiative feedback in either the host or nearby
halos created \hii~regions that encompass these halos.  For
\hii~regions without sustained star formation, these so-called relic
\hii~regions recombine and radiatively cool down to $T = 10^3$ K.
Within the virial radius, one can see that our simulations capture the
multi-phase ISM.  In the density projections, the effects of
photo-evaporation and cloud crushing are clearly seen, which are
caused by the stellar radiative and mechanical feedback, respectively.
The filaments adjacent to the halos are photo-heated to $T = 1-3
\times 10^4$ K, and then their gas escapes into the IGM no longer
being pressure equilibrium with the gravitational potential of the
filament, i.e. Jeans smoothing.  Furthermore, neighboring halos are
photo-evaporated \citep[see][for the level of halo
  photo-evaporation]{Wise08_Reion}, resulting in the suppression of
gas-rich satellite haloes.  A good illustration of photo-evaporation
in progress is the cometary structure in the bottom-center of the
density projection of Halo 4 at $z=7$.

%% \li Something is wrong with the progenitor finder with Halo 9 at $t =
%% 500$ Myr.  See the extreme jump in mass and decrease in gas fraction?

\subsubsection{Halo mass evolution}

\begin{figure}
  \plottwo{history0.eps}{history5.eps}
  \caption{\label{fig:massevo} Time evolution of the total halo mass
    (top panels), stellar mass (middle panels), and gas fraction
    (bottom panels; $M_{\rm gas} / M_{\rm tot}$) of the 10 most
    massive halos at $z=7$.  The cosmic mean gas fraction $\Omega_b /
    \Omega_M$ is marked by a horizontal dotted line in the bottom
    panels.}
\end{figure}

In the top panels of Fig. \ref{fig:massevo}, we show the total halo
mass $M_{\rm tot}$ of the most massive halos as a function of time.
We define the halo as a sphere with a radius $r_{200}$, centered on
the DM center-of-mass, with an overdensity of 200 times the cosmic
mean density.  The mass accretion histories of the halos are not
atypical from ones found in cosmological simulations with periods of
smooth accretion from the IGM and filaments with major mergers
occasionally occurs, appearing as jumps in $M_{\rm halo}(z)$.  The
halo mass histories are well described by the analytic expression
\citep{Wechsler02},
%
\begin{equation}
  \label{eqn:mhalo}
  M_{\rm halo}(a) = M_0 \exp \left[-2a_c\left(\frac{a_0}{a} -
    1\right)\right],
\end{equation}
%
where $a = 1/(1+z)$ is the scale factor, $M_0 = M_{\rm halo}(a_0)$,
and $a_c$ describes the rate of mass accretion.  The fitted values
values are listed in Table \ref{tab:halos} with $a_0 = 1/8$.

\subsubsection{Gas fraction evolution}

In the bottom panels of Fig. \ref{fig:massevo}, we show the gas
fraction $f_{\rm gas}(z) = M_{\rm gas} / M_{\rm tot}$ of these haloes.
The time evolution of the gas fraction is unique for each halo, but
there are some general trends.  Before any star formation occurs in
the halo, the gas fraction is near the cosmic fraction $\Omega_b /
\Omega_M$.  Then afterwards it decreases because one or more of the
three following processes (in order of decreasing impact): a PISN
explosion within the halo, Pop III stellar radiation within the halo,
and photo-evaporation from nearby star formation.  Cloud crushing due
to a nearby SN blastwave is also a possiblity if the halo mass is
small, but it is not as prevalent.  Complicating the scenario,
external feedback can also trigger star formation as they compress the
gas in the halo.  Even from the visual representations of the data in
Figs. \ref{fig:z7-mosaic}--\ref{fig:z10-mosaic}, it is clear that
almost all of the haloes and their environments are gas-poor with the
except of the most massive halo that resides in a cosmologically
overdense region.

In the most massive halo (Halo 0), \fgas~peaks at 0.19 at $z \sim 13$
because of a SN blastwave overrunning the halo and compressing the
gas.  This blastwave enriches the halo and triggers Pop II star
formation at $z=12$.  The ensuing radiative and mechanical feedback
drives outflows from the halo, reducing \fgas~by half to 0.08 over 100
Myr.  Afterwards this halo experiences a series of minor mergers and
two major mergers with gas-rich haloes, raising \fgas~to 0.15 by
$z=7$.  Halo 8 shows a similar recovery after a Pop III star forms and
its associated PISN explodes at $z \sim 12$, driving \fgas~from 0.15
to 0.01.  It slowly increases over the following 350 Myr to $\fgas =
0.14$ at $z=7$ because of gas-rich mergers.  The other eight haloes
remain relatively gas-poor ($0.05 \la \fgas \la 0.1$) after their
first epoch of star formation.

Because of the severity of gas loss from outflows created by Pop III
stars and Jeans-smoothing of the adjacent filaments, the halo is
dependent on mergers to replenish their gas supply
\citep[cf.][]{Yoshida07, Wise08_Gal, Greif10}.  For a halo to accrete
from a pre-heated IGM at a given time, it must exceed the `filtering
mass' \citep{Hui98, Gnedin00},
%
\begin{equation}
  \label{eqn:filtering}
  M_{\rm F}^{2/3} = \frac{3}{a} \int^a_0 da^\prime M_{\rm J}^{2/3}(a^\prime)
  \left[ 1 - \left(\frac{a^\prime}{a}\right)^{1/2} \right],
\end{equation}
where $M_{\rm J}$ is the time-dependent Jeans mass in the IGM.  We
plot $M_{\rm F}$ in the pre-heated IGM\footnote{We define the
  pre-heated IGM as regions with $x_e > 10^{-3}$ and $\rho/\bar{\rho}
  < 10$, where $x_e$ is the electron fraction and $\bar{\rho}$ is the
  mean cosmic density.} in Figure \ref{fig:filtering}.  Because the
haloes that merge into Halo 0 had $M > M_{\rm F}$, its gas fraction
recovers to nearly the cosmic fraction.  In contrast, all of the other
massive haloes build up their masses through mergers with halos $M \la
M_{\rm F}$ that cannot accrete from the pre-heated IGM.

Halo 8 is an uncommon case of a halo with a high gas accretion rate.
The merging haloes are still gas-rich because they have not hosted any
(including Pop III) star formation.  They lie in the outskirts of the
overdense region in the lower-right corner of the projections in
Fig. \ref{fig:evo-mosaic}.  It is 4.5 proper kpc from Halo 0 at $z=7$,
far enough away from the starbursting galaxies (the progenitors of
Halo 0) to avoid significant photo-evaporation but is subjected to
strong LW radiation, suppressing Pop III star formation.

\subsubsection{Star formation histories}

\subsubsection{Metallicity distribution function}

\subsubsection{Star formation rates}

@@

%% \subsection{Negative feedback}
%% \subsubsection{Gas loss from stellar feedback}
%% \subsubsection{Lyman-Werner radiation}
